Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-27 TACAS2018/paper.tex
modified the CEGIS figure

\begin{figure}[t!]
{
 \centering
 \scriptsize
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.8cm, column sep=1.5cm] {
  \coordinate (aux1);\&\&
  \coordinate (aux2);
  \coordinate (aux3) at ([xshift=3cm]aux2); \\
  \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model1) {{\sc 1. Abstract}};
  \& complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=9cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Model~~~~~~~~~~~},] (model) {};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Optimise}};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model3) at ([xshift=0cm]model.center) {{\sc 6. Refine}\\{\sc Abstraction}};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model4) at ([xshift=3cm]model.center) {{\sc 8. Sample}};
   } ;\\
   \node[minimum width=2.2cm, minimum height=0.8cm, fill=purple!20] (synth) {{\sc 2. Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=9cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify~~~~~~~~~~~},] (verif) {};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 3. Verify}\\{\sc Synthesis}};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 5. Discrete}\\{\sc Time}};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif3) at ([xshift=3cm]verif.center) {{\sc 7. Continuous}\\{\sc Time}};
   } 
   \& \coordinate (done);\\
   \& \\
   \node[minimum width=2.2cm, minimum height=0.8cm] (gp) {{\sf Program}\\{\sf Search}};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node[minimum width=2.2cm, minimum height=0.8cm] (bmc) at ([xshift=-3cm]aux.center) {\sf Eigensolver};
   \node[minimum width=2.2cm, minimum height=0.8cm] (fp)  at ([xshift=0cm]aux.center) {\sf Reachability \\ \sf Analysis};
   \node[minimum width=2.2cm, minimum height=0.8cm] (sv)  at ([xshift=3cm]aux.center) {\sf Reachability \\ \sf Analysis};
   }   
    \\
  };
   \path
    (synth.east) edge node[xshift=-0.5em,align=center] {$\mat{K}$,$\mat{L}$} (verif1.west)
    (verif1.east) edge node {PASS} (verif2.west)
    (verif2.north) edge node[xshift=.8cm] {C-ex} (model3.south)
    (verif2.east) edge node {PASS} (verif3.west)
    (verif3.north) edge node {C-ex} (model4.south)
    (model3.west) edge node {$k$,$X_0'$} (model2.east)
    (model4.west) edge node {$T_s$} (model3.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif3.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$\mat{A}'$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$\mat{A}'$,$\mat{B}'$,$\phi$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {{$\mat{A}$,$\mat{B}$,$\mat{C}$}\\{$\mat{A}'$,$\mat{B}'$,$\phi$}} ([xshift=5em]sv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif1.south)
    (verif3.east) edge node {PASS} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {FAIL/\\$\mat{K}$,$\mat{L}$} ([xshift=-5em]synth.south)
   ([xshift=5em]model1.south) edge node[align=center,xshift=-.7cm] {$\mathbb{R}_{\langle P \rangle}$} 
([xshift=5em]synth.north)
   node[align=left,yshift=-0.7cm,xshift=.5cm] {{$\phi$}\\{$\phi_{init}^K$}} %{$\phi_{safety}$}\\ 
   ([xshift=-5em]synth.north) edge node[align=center] {FAIL} ([xshift=-5em]model1.south);
   \path[->]
    ([xshift=-5em]verif1.north) edge node[align=center]  {C-ex} ([xshift=-5em]model2.south)
    ([xshift=5em]model2.south) edge node[align=center]  {$\mat{K}'$,$\mat{L}'$} ([xshift=5em]verif1.north)
    (model2.west) edge node[align=center] {$\phi$} (model1.east);

>>>>

\begin{figure}[t!]
{
 \centering
 \scriptsize
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.8cm, column sep=1.5cm] {
  \coordinate (aux1);\&\&
  \coordinate (aux2);
  \coordinate (aux3) at ([xshift=3cm]aux2); \\
  \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model1) {{\sc 1. Abstract}};
  \& complexnode/.pic={
    \coordinate (model);
    \node[minimum width=2.2cm, minimum height=0.8cm, fill=orange!20] (model2) at ([xshift=-3cm]model.center) {{\sc 4. Refine Abstraction}\\{\sc and Optimise}};
     \coordinate (model3) at ([xshift=0cm]model.center);
     \coordinate (model4) at ([xshift=3cm]model.center);
   } ;\\
   \node[minimum width=2.2cm, minimum height=0.8cm, fill=purple!20] (synth) {{\sc 2. Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=9cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify~~~~~~~~~~~},] (verif) {};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif1) at ([xshift=-3cm]verif.center) {{\sc 3. Verify}\\{\sc Synthesis}};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 5. Discrete}\\{\sc Time}};
     \node[minimum width=2.2cm, minimum height=0.8cm, fill=blue!20] (verif3) at ([xshift=3cm]verif.center) {{\sc 7. Continuous}\\{\sc Time}};
   } 
   \& \coordinate (done);\\
   \& \\
   \node[minimum width=2.2cm, minimum height=0.8cm] (gp) {{\sf Program}\\{\sf Search}};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node[minimum width=2.2cm, minimum height=0.8cm] (bmc) at ([xshift=-3cm]aux.center) {\sf Eigensolver};
   \node[minimum width=2.2cm, minimum height=0.8cm] (fp)  at ([xshift=0cm]aux.center) {\sf Reachability \\ \sf Analysis};
   \node[minimum width=2.2cm, minimum height=0.8cm] (sv)  at ([xshift=3cm]aux.center) {\sf Reachability \\ \sf Analysis};
   }   
    \\
  };
   \path
    (synth.east) edge node[xshift=-0.5em,align=center] {$\mat{K}$,$\mat{L}$} (verif1.west)
    (verif1.east) edge node {PASS} (verif2.west)
    (verif2.north) edge node[xshift=.8cm] {C-ex} (model3.south)
    (verif2.east) edge node {PASS} (verif3.west)
    (verif3.north) edge[-] node {C-ex} (model4.south)
    %(model2.west) edge node {$k$,$X_0'$} (model2.east)
    (model4.west) edge node {} (model2.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif3.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$\mat{A}'$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$\mat{A}'$,$\mat{B}'$,$\phi$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {{$\mat{A}$,$\mat{B}$,$\mat{C}$}\\{$\mat{A}'$,$\mat{B}'$,$\phi$}} ([xshift=5em]sv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {PASS/\\C-ex} ([xshift=-5em]verif1.south)
    (verif3.east) edge node {PASS} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {FAIL/\\$\mat{K}$,$\mat{L}$} ([xshift=-5em]synth.south)
   ([xshift=5em]model1.south) edge node[align=center,xshift=-.7cm] {$\mathbb{R}_{\langle P \rangle}$} 
([xshift=5em]synth.north)
   node[align=left,yshift=-0.7cm,xshift=.5cm] {{$\phi$}\\{$\phi_{init}^K$}} %{$\phi_{safety}$}\\ 
   ([xshift=-5em]synth.north) edge node[align=center] {FAIL} ([xshift=-5em]model1.south);
   \path[->]
    ([xshift=-5em]verif1.north) edge node[align=center]  {C-ex} ([xshift=-5em]model2.south)
    ([xshift=5em]model2.south) edge node[align=center]  {$\mat{K}'$,$\mat{L}'$} ([xshift=5em]verif1.north)
    (model2.west) edge node[align=center] {$\phi$} (model1.east);
